\documentclass[margin,line]{resume}

\paperheight=-0.1in
%\addtolength{\textwidth}{.5in}
%\addtolength{\textheight}{.5in}

\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{bbding}
\usepackage[colorlinks]{hyperref}
\usepackage{color}

\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{colorlinks, linkcolor=darkblue, filecolor=darkblue, urlcolor=black, citecolor=darkblue}

\begin{document}
\name{\Large Dr. sc. Gerd Zellweger}
\begin{resume}

% Contact Information
\section{\mysidestyle Contact\\Information}

\begin{tabularx}{\textwidth}{lXcl}
CSF1083F\\
3401 Hillview Ave     & & \raisebox{-3pt}{\Phone}    & +1 650 427 2317 \\
Palo Alto, CA 94304, USA   & & \raisebox{-3pt}{\Envelope} & gzellweger@vmware.com \\
\end{tabularx}

% Research Interests
%\section{\mysidestyle Research\\Interests}
%Operating Systems....

% Education
\section{\mysidestyle  Education}

\textbf{ETH Zürich}, Switzerland \vspace{2mm}\\\vspace{1mm}%
\textsl{Doctor of Sciences ETH Zurich} \hfill \textbf{2013 -- 2017}\vspace{-3mm}\\\vspace{-1mm}%
\begin{list2}
    \item Dissertation ``On the Construction of Dynamic and Adaptive Operating Systems''
    \item Advisor: Professor Timothy Roscoe
\end{list2}\vspace{-1.5mm}

\textsl{Master of Science in Computer Science} \hfill \textbf{2009 -- 2012}\vspace{-3mm}\\\vspace{-1mm}%
\begin{list2}
    \item Focus: Distributed Systems
    \item Advisor: Professor Timothy Roscoe
\end{list2}\vspace{-1.5mm}

\textsl{Bachelor of Science in Computer Science} \hfill \textbf{2006 -- 2010}\vspace{-3mm}\\\vspace{-1mm}%

%\textbf{Kantonsschule Obwalden}, Switzerland \vspace{2mm}\\\vspace{1mm}%
%\textsl{Focus in physics and applied mathematics} \hfill \textbf{2000 --
%2006}\vspace{-3mm}\\\vspace{-1mm}%


% Professional Experience
\section{\mysidestyle Professional\\Experience}

\textbf{VMware, Research Group}, Palo Alto, USA \vspace{2mm}\\\vspace{1mm}%
\textsl{Research Scientist} \hfill \textbf{March 2018 -- now}\\
Exploring operating systems design and implementation, networks
and system software interaction with emerging hardware technologies.

\textbf{ETH Zürich}, Zürich, CH \vspace{2mm}\\\vspace{1mm}%
\textsl{Research Assistant} \hfill \textbf{February 2013 -- December 2017}\\
Doctoral student doing research on how to structure an OS for future multi and 
many-core systems. Teaching operating systems, networks, parallel- and systems programming 
to graduate and under-graduate students.
% ETH Zurich, Rämistrasse 101, 8092 Zürich, Switzerland
% Simonetta Zysset, +41 44 632 68 79
% 1.2.2013 -- 31.12.2017

\textbf{HP Labs}, Palo Alto, USA \vspace{2mm}\\\vspace{1mm}%
\textsl{Research Associate} \hfill \textbf{June 2015 -- September 2015}\\
I worked in the systems research group where I designed, implemented and
evaluated extensions to the virtual memory subsystem for a BSD derivative OS,
to address problems occurring with huge memory capacities in high-end server
systems.\\ Technologies: C, virtual memory systems

%% 01/06/15 – 09/15/15
%% Manager: Dejan Milojicic
%% HP Labs
%% 1501 Page Mill Road
%% Palo Alto, CA 94304-1126 
%% Phone: 650-857-1501

\textbf{Microsoft Research}, Redmond, USA \vspace{2mm}\\\vspace{1mm}%
\textsl{Research Intern} \hfill \textbf{July 2014 -- September 2014}\\
I collaborated with the Orleans team to work on the Orleans
actor system, a distributed runtime for the cloud. I looked specifically at
actor placement algorithms and developed new algorithms to improve the actor placement
decisions and evaluated them in the cloud.\\ Technologies: C\#, .NET, Azure Cloud, Orleans

%% 06/16/14 – 09/12/14
%% Manager: Gabriel Kliot, now at Google
%% Microsoft Research, Redmond, USA
%% 14865 NE 36th St, Redmond, WA 98052
%% Phone: +20 2 27689700

\textbf{sc-n.ch}, Zürich, Switzerland \vspace{2mm}\\\vspace{1mm}%
\textsl{Software Engineer} \hfill \textbf{February 2012 -- February 2013}\\
Consultant working for a large insurance company (Java EE, IBM Websphere, Ant, XML, SOA).
%I was working as a consultant, for a large insurance company in Switzerland to
%assist in the migration of their SOA landscape from J2EE 1.4 and Java EE 5 to
%Java EE 6. As a member of the technical architecture team, I was helping
%developers with the migration of their codebase and troubleshooting the bugs
%that appeared as a result of the migration. I was also doing the migration for
%some of the core technical services of the company.\\ Technologies: Java, Java
%EE, IBM Websphere, Ant, XML, SOA

%% Contat: Erich Bleiker, sc-n.ch

\textbf{Capgemini sd\&m}, Zürich, Switzerland \vspace{2mm}\\\vspace{1mm}%
\textsl{Working Student} \hfill \textbf{September 2008 -- December 2008}\\
%\textsl{Developer Intern} \hfill \textbf{June 2008 -- September 2008}\\

%I continued working on the released version of the project environment (see
%internship below) and did most of the bug fixing. In addition, I helped to
%develop an Eclipse plugin, which aimed at providing teams with homogeneous
%configurations for their IDE and respective plugins.

%I worked in a team to develop a new version of the company's own project
%environment. My work consisted of providing RPM packages for new and updated
%modules, writing scripts for automatic migration and installation, and an
%application for snapshot generation to aid with the generation of RPM
%packages. My work also included bug fixing and test case creation for various
%applications.

%\textbf{EFPE}, Dortmund, Germany \vspace{2mm}\\\vspace{1mm}%
%\textsl{Freelancer} \hfill \textbf{2006 -- Now}\\
%I created the website for the company and developed an application to help
%them manage their client relations. Today I am responsible for their servers
%and maintain the software.\\
%Technologies: Python, Django, GTK, MySQL, Linux

\pagebreak

% Computer Skills
\section{\mysidestyle Peer-reviewed Publications}

Igor Smolyar, Alex Markuze, Boris Pismenny, Haggai Eran, Gerd Zellweger, Austin Bolen, Liran Liss, Adam Morrison, Dan Tsafrir.
``\textbf{IOctopus: outsmarting nonuniform DMA.}'', \textsl{Conference on Architectural support for Programming languages and Operating systems (ASPLOS)}, Lausanne, CH, March 2020 [best paper award].

Gerd Zellweger, Denny Lin, Timothy Roscoe.
``\textbf{So many performance events, so little time}'', \textsl{Proceedings of the 7th Asia-Pacific Workshop on Systems (APSys)}, Hong Kong, China, August 2016.

Jana Giceva, Gerd Zellweger, Gustavo Alonso, Timothy Roscoe.
``\textbf{Customized OS support for data processing}'',
\textsl{Proceedings of the 12th International Workshop on Data Management on New Hardware (DaMoN)}, San Francisco, USA, June 2016.

Jana Giceva, Gerd Zellweger, Gustavo Alonso, Timothy Roscoe.
``\textbf{Basslet: an OS runtime for parallel data processing}'',
\textsl{Workshop on Multicore and Rack-scale Systems (MaRS)}, London, UK, April 2016 [extended abstract \& talk].

Izzat El Hajj, Alexander Merritt, Gerd Zellweger, Dejan Milojicic, Reto Achermann, Paolo Faraboschi, Wen-mei Hwu, Timothy Roscoe, Karsten Schwan.
``\textbf{SpaceJMP: Programming with Multiple Virtual Address Spaces}'',  \textsl{Proceedings of the 21th international conference on Architectural support for Programming languages and Operating systems (ASPLOS)}, Atlanta (GA), USA, April 2016 [HiPEAC paper award].

Simon Gerber, Gerd Zellweger, Reto Achermann, Kornilios Kourtis, Timothy Roscoe, Dejan Milojicic.
``\textbf{Not Your Parents' Physical Address Space}'', \textsl{Proceedings of the 15th Workshop on Hot Topics in Operating Systems (HotOS)}, Kartause Ittingen, May 2015.

Gerd Zellweger, Simon Gerber, Kornilios Kourtis, Timothy Roscoe.
``\textbf{Decoupling Cores, Kernels, and Operating Systems}'',
\textsl{Proceedings of the 11th USENIX Symposium on Operating Systems Design and Implementation (OSDI)}, Broomfield, USA, October 2014.

Gerd Zellweger, Adrian Schüpbach, Timothy Roscoe.
``\textbf{Unifying synchronization and events in a multicore OS}'',
\textsl{Proceedings of the 3rd Asia-Pacific Workshop on Systems (APSys)}, Seoul, South Korea, July 2012.

%Gerd Zellweger.
%``\textbf{Unifying synchronization and events in a multicore OS}'',
%\textsl{Master's thesis}, ETH Zurich, March 2012.


\section{\mysidestyle Patents}

Izzat El Hajj, Alexander Merritt, Gerd Zellweger, Dejan Milojicic.
\textbf{Persistent virtual address spaces}, PCT/US2016/015661, submission
pending, filed Jan. 29, 2016.

Izzat El Hajj, Alexander Merritt, Gerd Zellweger, Dejan Milojicic.
\textbf{Versioning virtual address spaces}, PCT/US2016/015814, submission
pending, filed Jan. 29, 2016.

Izzat El Hajj, Alexander Merritt, Gerd Zellweger, Dejan Milojicic.
\textbf{Identifying object modifications}, PCT/US2016/015815, submission
pending, filed Jan. 29, 2016.

Izzat El Hajj, Alexander Merritt, Gerd Zellweger, Dejan Milojicic, Reto
Achermann. \textbf{Memory management with versioning of objects},
PCT/US2016/015839, submission pending, filed Jan. 29, 2016.

Izzat El Hajj, Alexander Merritt, Gerd Zellweger, Dejan Milojicic.
\textbf{Switch process virtual address space}, PCT/US2015/049726, submission
pending, filed Sept. 11, 2015.

\pagebreak

% Projects
\section{\mysidestyle Projects}
\textbf{{\TeX}ercises} \\\vspace{1mm}%
%\textsl{\url{www.texercises.com}} \hfill \\
I was a co-founder of Texercises, a company that provides a collaborative online
exercise database for all kinds of classes in science of nature and allows
simple and quick generation of exercise sheets for teachers and students. I was
responsible for the technical development of the product. Texercises was
acquired by edTechLab AG in 2015.\\
Technologies: Python, Django, SQL, JavaScript, LaTeX, HTML

\textbf{Barrelfish OS} \\\vspace{1mm}%
\textsl{\url{www.barrelfish.org}} \hfill \\
The Barrelfish operating system is exploring how to structure an OS for future
multi- and many- core systems motivated by the increasing amount of cores and
diversity in computer hardware. I have contributed code to most areas of the
system during my studies at ETH and I have written some of the core services
and a few device drivers in the OS from scratch.\\ Technologies: C, Python,
Haskell, x86, ARM

\textbf{Open Source Software} \\\vspace{1mm}%
\textsl{\url{www.github.com/gz}} \hfill \\
I enjoy collaborating on open source projects. I am the creator and maintainer
of several open source libraries and programs, mainly written in Rust and
Python.

% Computer Skills
\section{\mysidestyle Teaching}

I have been a teaching assistant at ETH for Systems Programming and Computer
Architecture (2014, 2015, 2016), Parallel Programming (2014, 2015), Advanced
Operating Systems (2014) and Computer Science for Biology and Pharmaceutical
Sciences (2013). My duties involved weekly tutoring sessions with up to 30
students, devising and grading weekly exercises, midterm and end-term exams.

%\\
%\textsl{Programming & Problem solving} \hfill
%\textbf{SS 2016}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Systems Programming and Computer Architecture} \hfill
%\textbf{Autumn~2015}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Parallel Programming} \hfill
%\textbf{Spring~2015}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Systems Programming and Computer Architecture} \hfill
%\textbf{Autumn~2014}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Parallel Programming} \hfill
%\textbf{Spring~2014}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Advanced Operating Systems} \hfill
%\textbf{Autumn~2013}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Computer Science for Biology \& Pharmaceutical Sciences} \hfill
%\textbf{Autumn~2013}\vspace{-3mm}\\\vspace{-1mm}\\
%\textsl{Computer Science for Biology \& Pharmaceutical Sciences} \hfill
%\textbf{Spring~2013}\vspace{-3mm}\\\vspace{-1mm}\\

\section{\mysidestyle Invited Talks}

April 2017: \textbf{VMware Research} invited talk on \textit{``Implications of New and Future Hardware for Operating Systems''}\\
April 2017: \textbf{Apple CoreOS} invited talk on \textit{``Implications of New and Future Hardware for Operating Systems''}\\
April 2017: \textbf{HPE Labs} invited talk on \textit{``Implications of New and Future Hardware for Operating Systems''}\\
March 2017: \textbf{Microsoft Research} invited talk on \textit{``Implications of New and Future Hardware for Operating Systems''}\\
March 2017: \textbf{Huawei Research} invited talk on \textit{``Implications of New and Future Hardware for Operating Systems''}\\
January 2017: \textbf{ETH Zurich}, Industry Retreat talk on \textit{``The Paradox of Choice in Multicore Performance Monitoring''}\\
April 2016: \textbf{ASPLOS conference} Lightning talk on \textit{``SpaceJMP''}\\
January 2016: \textbf{ETH Zurich}, Industry Retreat talk on \textit{``SpaceJMP''}\\
November 2015: \textbf{ETH Zurich}, Department Evaluation on \textit{``Decoupling Cores Kernels and Operating Systems''}\\
October 2015: \textbf{NewOS Workshop}: On \textit{``Applications for HPC, IoT and non-volatile memory''}\\
September 2015: \textbf{ETH Zurich}, Lunch Seminar on \textit{``Multiple virtual address spaces''}\\
August 2015: \textbf{HP Labs} invited talk on \textit{``Multiple virtual address spaces''}\\
January 2015: \textbf{ETH Zurich}, Industry Retreat talk on \textit{``Decoupling Cores Kernels and Operating Systems''}\\
November 2014: \textbf{OSDI Conference} talk on \textit{``Decoupling Cores Kernels and Operating Systems''}\\
September 2014: \textbf{ETH Zurich}, Seminar talk on \textit{``Decoupling Cores Kernels and Operating Systems''}\\
March 2013: \textbf{ETH Zurich}, Seminar talk on \textit{``Device Management in a Multicore OS''}\\

% Computer Skills
\section{\mysidestyle Programming}

I taught myself programming using PHP as a teenager. Currently I'm most
comfortable using Python for scripting, C and Rust for low level programming and
Java for everything in between. In addition, I have some experience programming
in Haskell, Eiffel and C\#.

\section{\mysidestyle Service}
\textbf{Shadow PC} EuroSys 2017 %

% Languages
\section{\mysidestyle Languages}
\begin{list2}
    \item German: Native language
    \item English: Fluent in reading and writing
    \item French: Basic knowledge
\end{list2}\vspace{-1.5mm}

\pagebreak

% Referees
\section{\mysidestyle References}
{\sl Available on request.}

%\begin{tabular}{@{}p{8cm}p{8cm}}
%  \textbf{Timothy Roscoe}   				            &  \textbf{Boris Bluntschli}                      \\
%  Professor                                             &  Software Engineer                              \\
%  Department of Computer Science, ETH Zürich            &  Google                                         \\
%  Zürich, Switzerland                      		        &  Zürich, Switzerland                            \\
%  phone: \textsl{+41 44 632 88 40} 			            &  phone: \textsl{+41 79 798 02 51}               \\
%  e-mail: \textsl{timothy.roscoe@inf.ethz.ch}           &  e-mail: \textsl{boris.bluntschli@gmail.com}    \\
%\end{tabular}
%
%\begin{tabular}{@{}p{8cm}p{8cm}}
%  \textbf{Aseem Kishore}                                &  \textbf{Daniel Gasienica}                       \\
%  Developer at FiftyThree, Inc.                     &  Developer at FiftyThree, Inc.                   \\
%  Former Development Lead at Microsoft Live Labs        &  Former Software Engineer at Microsoft Live Labs \\
%  New York, USA                                          &  Seattle, USA                                    \\
%  phone: \textsl{+1 716 465 10 28}                        &  phone: \textsl{+1 404 981 42 74}                                \\
%  e-mail: \textsl{aseem.kishore@gmail.com}              &  e-mail: \textsl{daniel@gasienica.ch}            \\
%\end{tabular}

\end{resume}
\end{document}
